%!TEX root = ../main.tex

\section{Empirical Framework}\label{sec:empirical}

%=============================================================================
\subsection{Data}\label{sec:data}
%=============================================================================

We construct a daily panel spanning January~4, 2021 to March~17, 2026
(1,900 trading days) from six sources:

\paragraph{BTC prices.}
Daily BTC/USDT closing prices from Binance via CryptoDataDownload.
We use the USDT-denominated pair for liquidity and convert to USD at
the prevailing USDT peg (effectively 1:1 over our sample).

\paragraph{MSTR equity.}
Split-adjusted daily closing prices and shares outstanding from
Compustat.  Strategy executed a 10-for-1 stock split on August~8, 2024;
all per-share quantities are reported on a post-split basis.

\paragraph{BTC holdings.}
Strategy's disclosed BTC holdings, resampled to daily frequency via
forward-fill from the company's SEC filings and press releases.
As of March~17, 2026, holdings stand at 761,068~BTC.

\paragraph{BTC purchase history.}
Individual purchase events with dates, quantities (in BTC), and
dollar amounts, used to calibrate the jump component of holding
dynamics.  Strategy executed approximately 49 discrete purchases over
the sample period with a mean size of 7,044~BTC.

\paragraph{Balance sheet.}
Quarterly total debt from Compustat, forward-filled to daily.
Total debt as of March~2026: \$8.22B.

\paragraph{Preferred stock.}
Five series of perpetual preferred stock issued between 2025 and 2026,
with details shown in Table~\ref{tab:preferred}.

\begin{table}[H]
\centering
\caption{Strategy preferred stock detail (as of March 2026).}
\label{tab:preferred}
\begin{tabular}{@{}lccccc@{}}
\toprule
\textbf{Ticker} & \textbf{Div.\ Rate} & \textbf{Shares (M)} &
\textbf{Liq.\ Value (\$B)} & \textbf{Ann.\ Div.\ (\$M)} &
\textbf{Convertible} \\
\midrule
STRK  & 8.0\%  & 12.8  & 1.28  & 102   & Yes \\
STRF  & 10.0\% & 10.5  & 1.05  & 105   & No \\
STRC  & 9.6\%  & 50.0  & 5.00  & 479   & No \\
STRD  & 10.0\% & 25.0  & 2.50  & 250   & No \\
STRE  & 10.0\% &  5.0  & 0.40  &  40   & No \\
\midrule
\textbf{Total} & & 103.3 & 10.23 & 977 & \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Risk-free rate.}
Daily 3-month Treasury bill yields from the Federal Reserve
(secondary market rate), used as the risk-free rate $r_f$.

\paragraph{Panel construction.}
We align all series to the common daily index and compute:
\begin{itemize}
  \item Asset value: $A_t = H_t \cdot S_t$;
  \item NAV: $\mathrm{NAV}_t = (A_t - D_t - P_t^{\mathrm{liq}})^+$,
    clipped at a floor of \$1 for log-stability;
  \item Equity value: $E_t = P_t^{\mathrm{MSTR}} \times N_t^{\mathrm{sh}}$;
  \item Log-premium: $\pi_t = \log(E_t / \mathrm{NAV}_t)$;
  \item BTC per share: $B_t = H_t / N_t^{\mathrm{sh}}$.
\end{itemize}

We exclude observations where $\mathrm{NAV}_t \le 0$ or
$\mathrm{NAV}_t < \$100$M from the calibration subset, yielding
a clean sample for the OU estimation.

%=============================================================================
\subsection{Estimation}\label{sec:estimation}
%=============================================================================

%-----------------------------------------------------------------------------
\subsubsection{BTC Volatility}
%-----------------------------------------------------------------------------

We estimate annualised BTC volatility from daily log-returns:
\begin{equation}
  \hat\sigma_S = \mathrm{std}(\Delta\log S_t) \times \sqrt{252}.
\end{equation}

%-----------------------------------------------------------------------------
\subsubsection{OU Premium Dynamics}
%-----------------------------------------------------------------------------

We fit the log-premium $\pi_t$ to an Ornstein--Uhlenbeck process via
AR(1) regression.  Discretising $d\pi_t = \kappa(\theta - \pi_t)\,dt
+ \sigma_\pi\,dW_t^\pi$ at daily frequency ($\Delta t = 1/252$):
\begin{equation}
  \pi_{t+\Delta t} = a + b\,\pi_t + \varepsilon_t,
  \qquad \varepsilon_t \sim \mathcal{N}(0, \sigma_\varepsilon^2),
\end{equation}
where $b = e^{-\kappa\Delta t}$, $a = \theta(1-b)$, and
$\sigma_\varepsilon^2 = \sigma_\pi^2(1 - e^{-2\kappa\Delta t})/(2\kappa)$.
We recover:
\begin{equation}
  \hat\kappa = -\frac{\log\hat{b}}{\Delta t},
  \quad
  \hat\theta = \frac{\hat{a}}{1-\hat{b}},
  \quad
  \hat\sigma_\pi = \hat\sigma_\varepsilon
    \sqrt{\frac{2\hat\kappa}{1 - e^{-2\hat\kappa\Delta t}}}.
\end{equation}

%-----------------------------------------------------------------------------
\subsubsection{Correlation Structure}
%-----------------------------------------------------------------------------

The correlation $\hat\rho$ between BTC log-returns and premium innovations
is estimated from the OLS residuals.  The premium sensitivity
$\hat\gamma_{\pi S}$ is the regression coefficient of $\Delta\pi_t$ on
$\Delta\log S_t$.

%-----------------------------------------------------------------------------
\subsubsection{Holdings Dynamics}
%-----------------------------------------------------------------------------

The holding process $dH_t = \alpha\pi_t^+\,dt + dH_t^{\mathrm{jump}}$
is calibrated by:
\begin{enumerate}
  \item Estimating the continuous component $\hat\alpha$ from the regression
    of non-jump holding changes on $\pi_t^+$.
  \item Identifying discrete purchase events (jumps) and estimating
    arrival rate $\hat\lambda_M$ (events per year) and mean jump size
    $\mathbb{E}[\Delta H]$ from the purchase history.
\end{enumerate}

%=============================================================================
\subsection{Capital Structure}\label{sec:capstruct_empirical}
%=============================================================================

Strategy's capital structure as of March~2026 comprises four layers
in strict priority:

\begin{enumerate}
  \item \textbf{Senior debt:} \$8.22B in convertible senior notes,
    weighted average coupon 0.42\%.  The 0\% notes due 2029 (\$3B,
    conversion at \$672.40) and 2030 (\$2B, conversion at \$433.43)
    dominate.  Notes with conversion prices below \$250 are deep
    in-the-money and model as quasi-equity.
  \item \textbf{Non-convertible preferred:} STRF, STRC, STRD, STRE
    with combined liquidation value of \$8.95B and annual dividends
    of \$874M.  These are perpetual fixed obligations.
  \item \textbf{Convertible preferred:} STRK with \$1.28B liquidation
    value, 8\% dividend, and conversion at \$1,000/share (currently
    deep out-of-the-money at MSTR $\approx$\$150).
  \item \textbf{Common equity:} 320.4M shares outstanding with
    residual claim on $\mathrm{NAV}_t = (A_t - D_t - P_t^{\mathrm{liq}})^+$.
\end{enumerate}

The total liquidation value of preferred stock is \$10.23B, creating
a preferred-plus-debt obligation of \$18.45B.  The annual preferred
dividend of \$977M represents the dominant fixed-cost burden and is
the binding constraint in the leverage spiral analysis.

Remaining issuance capacity: \$8.1B common equity ATM, \$20.3B STRK,
\$3.6B STRC, \$4.2B STRD, \$2.1B STRF.  This capacity provides
optionality for future BTC acquisition across premium regimes.
